---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rosario

<!-- badges: start -->
<!-- badges: end -->

This R package implements two common measures of overlap in resource use for communities. We implement the Pianka (Pianka 1973) and Czekanowski indices (Feinsinger, Spears, & Poole 1981).


We implement the Pianka's index of overlap as:

$$
\alpha_{j, k} = \frac{ \sum_{i = 1}^{n}p_{ij}p_{ik} }{\sqrt{} \sum_{i = 1}^{n}p_{ij}^2 * \sum_{i = 1}^{n} p_{ik}^2 }
$$
As well as the Czekanowski index of overlap.
$$
\alpha_{j, k} = 1 -\frac{1}{2}\Big(\sum_{i = 1}^{n} |p_{ij} - p_{ik}| \Big)
$$



## Installation

You can install the development version of rosario hosted in github:

``` r
devtools::install_github("alrobles/rosario")
```

## Example

In this case of  use we  create a simulated community with 20 species and 300 time intervales. With a Poisson distribution.
We rescale to get que relative frequency of time counts and
get both distance


```{r example}
library(rosario)
## basic example code
n = 200
k = 1440
#create random matrix
m = matrix(rpois(n*k, 10), ncol = k)


# rescale with sum of rows
m <- rosario::rescale_matrix(m)

nm <- rosario::get_null_model(m, "pianka")
# load rosario R package
library(rosario)

m_overlap <- temp_overlap_matrix(m, method = "pianka")
m_overlap_df <- temp_overlap_df(m_overlap)

# measure the overlap matrix with Pianka's method
overlap_pianka <- temp_overlap(m, method = "pianka")

# measure the overlap matrix with Czekanowski method
overlap_czekanowski <- temp_overlap(m, method = "czekanowski")
```

We can observe the first 6 rows between species:

```{r}
overlap_pianka
```


<!-- And for the second example: -->

<!-- ```{r} -->
<!-- overlap_czekanowski[1:6, 1:6] -->
```


